{\Large Abstract}\\
\hrule

% [Explain the need/uses]
Many systems require a camera to identify the objects in its field of view, and then rotate the camera to keep it aimed at a certain type of object. Examples of this need include filming cheetahs to further research into bio-mimicry, having a quadcopter record and follow a sports-person as they move around, and helping wildlife parks to spot and track poachers before they can cause harm.

% [Paragraph on computer vision]
Luckily, the field of computer vision has seen a recent surge in performance - in fact, methods such as neural networks often achieve higher accuracy scores than humans in tasks such as object detection. The technology is in general very accessible, with a strong culture of open-research and open-source.

% [Paragraph on raspberry pi + NCS]
However, image recognition using neural networks is an extremely compute intensive task. The nature of the computation suits parallelization, but inferring a result from an underpowered mobile device (such as a raspberry pi, which is a type of single board computer) can take a full second or longer. Again there exists a solution: neural accelerators, which are essentially GPUs on USB sticks. These enable object recognition in near real-time.

% [Paragraph on EKF]
Despite the speed-ups offered by neural accelerator sticks, the maximum number of inferences possible per second is still somewhat low. In this respect, the Kalman Filter can be useful. It enables the computer to predict where the tracked object will be in between updates from the neural network.

Thus, the aim of this project is as follows: using a modern neural network architecture, identify and track cheetahs from a mobile platform. The computing power is limited (a Raspberry Pi and Movidius Neural Compute Stick) which results in slow update rates. In addition, only position is measured. Thus, a Kalman Filter is used to help ensure robust and smooth tracking of the target. In order to rotate the camera and the rest of the payload, a gimbal was also designed.

\newpage
