\documentclass{article}

\usepackage{graphicx}

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\begin{document}
\title{Alex Thesis Project}
\author{Alexander Knemeyer}

\maketitle

\pagenumbering{gobble}  % turn off page numbering

\newpage

\pagenumbering{roman}

\begin{abstract}
% [Explain the need/uses]
Many systems require a camera to identify the objects in it's field of view, and then move the camera to keep it aimed at a certain type of object. Examples of this need include filming cheetahs to further research into bio-mimicry, having a quadcopter record and follow a sportsperson as they move around and helping wildlife parks to spot and track poachers before they can cause harm.

% [Paragraph on computer vision]
Luckily, there has been a recent surge in performance for computer vision techniques. Neural networks often achieve higher accuracy scores than humans in tasks such as object detection. The technology is in general very accessible, with a strong culture of open-research and open-source.

% [Paragraph on raspberry pi + NCS]
However, image recognition using neural networks is an extremely compute intensive task. The nature of the computation suits parallelisation, but inferring a result from an underpowered mobile device (such as a raspberry pi, which is a type of single board computer) can take a full second or longer. Again, there exists a solution: neural accelerators, which are essentially a GPU on a USB stick. These enable object recognition in near real-time.

% [Paragraph on EKF]
Despite the speedups offered by neural accelerator sticks, the maximum number of inferences possible per second is still somewhat low. In this respect, the Kalman Filter can be useful. It enables the computer to predict where the tracked object will be in between updates from the neural network.

Thus, the aim of this project is as follows: using a modern neural network architecture, identify and track cheetahs from a mobile platform. The computing power is limited (a Raspberry Pi and Movidius Neural Compute Stick) which results in slow update rates. In addition, only position is measured. Thus, an Extended Kalman Filter is used to help ensure robust and smooth tracking of the target.
\end{abstract}

\newpage

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\section*{Terms of Reference}

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\section*{Acknowledgement}
thanks Callen and Amir \\
thanks Justin Pead \\
thanks Stacey for laser cutting \\
thanks family and friends

\newpage

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\tableofcontents
\newpage

\listoffigures
\listoftables

\newpage

\pagenumbering{arabic}

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\input{introduction/introduction.tex}

\newpage

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\input{literature_review/literature_review.tex}

\newpage

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\input{research_design_and_timeline/research_design_and_timeline.tex}

\newpage

%-----------------------------------------------------------------------
%-----------------------------------------------------------------------
%-----------------------------------------------------------------------

\input{system_modelling_and_design/system_modelling_and_design.tex}

\section{System Integration and Testing}

\section{Results}
DONT DISCUSS THE RESULTS, JUST SHOW THEM!

\section{Discussion}
THIS IS THE ONLY SECTION WHERE THE RESULTS ARE DISCUSSED

\section{Conclusions}
test text

\section{Recommendations and Future Work}
Talk about: \\
- do other objects/animals \\
- predict distance with nn afterwards (using gopro footage)

\section{References}

\appendix
\section{Additional Files and etc etc}

\section{Addenda}
\subsection{Ethics Forms}

% ----------------------------------------------------------------
\end{document}
